---
title: "Summary data"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(googlesheets4)
library(magrittr)
library(dplyr)
```

```{r}
df <- read_sheet("18uicdDpHg2YNIQ6eAyGsKrvrwu1G4Rr6eiSVUlGX-CY", skip = 1, na=c("", "NA")) %>%
  mutate(Condition = tolower(Condition)) %>% 
  rename(Disease = `Disease/Disorder/Syndrome`)

df_filtered <- df %>%
  filter(Link_active) %>%
  filter(English) %>% 
  mutate(life = fertility | pregnancy | birth | aging | end_of_life,
         individual = symptoms | risk_factors)

condition <- df_filtered %>%
  distinct(Condition, Chronic_Condition_CMS, Disease)


events_life <- df_filtered %>% filter(fertility | pregnancy | birth | aging | end_of_life)
events_ind <- df_filtered %>% filter(symptoms | risk_factors)
```

# Data summary

Data were collected from two decision aid repositories: the [Ottawa Hospital Research Institute (OHRI) Patient Decision Aid](https://decisionaid.ohri.ca/) library and the [Mayo Clinic's Knowledge and Evaluation Research Unit (Mayo)](https://www.mayo.edu/research/labs/knowledge-evaluation-research-unit/overview). Jointly, the libraries contain `r nrow(df)` decision aids. Researchers filtered out decision aids that have inactive links. Additionally, decision aids were excluded if they are not available in English, resulting in a sample of size of `r nrow(df_filtered)`. 

```{r}
designers <- df_filtered %>% 
  group_by(Designer) %>% 
  tally() %>% 
  arrange(desc(n))
```

The resulting sample of decision aids were creating overwhelmingly by one developer, Healthwise. Healthwise represents `r round(designers %>% slice(1) %>% pull(n)*100/nrow(df_filtered), 1)`% of the data subset. The developer that represents the second largest proportion of the sample is Mayo Clinic (`r round(designers %>% slice(2) %>% pull(n)*100/nrow(df_filtered), 1)`%).

## Health Conditions

The decision aids database includes a diverse set of health conditions (n = `r condition %>% nrow()`), that vary from life-threatening illnesses such as cancer, temporary health situations such as pregnancy and behavioral health choices such as contraception. The term *health condition* is used to communicate a state of health that deviates for a health norm. Health conditions vary widely, encompassing states of health such as pregnancy as well as diseases such as depression and heart disease. Diseases, disorders, and syndromes are a subset of health conditions (n = `r condition %>% filter(Disease) %>% nrow()`). Of the `r condition %>% nrow()` conditions represented in the data, `r condition %>% filter(Chronic_Condition_CMS) %>% nrow()` can be categorized as chronic conditions under the [Centers for Medicaid and Medicare's classification system](https://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Chronic-Conditions/CC_Main).

### Types of Decisions

```{r, eval = FALSE}

set.seed(1234)

df_filtered %>% group_by(Condition) %>% sample_n(1) %>%
  group_by(Designer) %>% 
  tally() %>% 
  arrange(desc(n))

nh <- df_filtered %>% 
  filter(Designer != "Healthwise") %>% 
  group_by(Condition) %>% 
  sample_n(1)

h <- df_filtered %>% 
  filter(Designer == "Healthwise") %>% 
  filter(!(Condition %in% nh$Condition)) %>%
  group_by(Condition) %>% 
  sample_n(1)

sample <- nh %>%
  bind_rows(h) %>%
  arrange(Condition)

df <- df %>% 
  mutate(sample = id %in% sample$id)

```


